---
title: "homework-number-5"
output: html_document
---
```{r}
library(curl)
library(knitr)
library(boot)
```
```{r}
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall17/KamilarAndCooperData.csv")
df <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(df)
```
#1
```{r}
h <- log(df$HomeRange_km2)

b <- log(df$Body_mass_female_mean)
```

```{r}
plot(x = b, y = h)
```
Here I plotted  log(HomeRange_km2) and log(Body_mass_female_mean) so see the relation

```{r}
m <- lm(data = df, h ~ b)
summary(m)
```
Here the intercept is -9.44123 and the slope is 1.03643

#2
```{r}
k <- 1000  # number of samples
n <- 5   #the homeworkd didnt say how big to make each sample so I just used 5
s <- NULL  # dummy variable to hold each sample
for (i in 1:k) {
    s[[i]] <- sample(m, size = n, replace = FALSE)
}
head(s[[i]])
```
```{r}
summary(s)
```
im going to try and use the boot package and fallowing the steps in the book to see if this is how I should make it
```{r}
bs <- function(formula = lm(h ~b), data, indices) {
  d <- data[indices]
  fit <- lm(formula, data=d)
  return(coef(fit))
}
```

```{r, eval=FALSE}
results <- boot(data=df, statistic=bs, R=1000, formula = lm(h ~ b))
```
I am still working on figuring this out so it might take longer than 2 pm today, but I'll submit what I have now and again when I finish it. Sorry for the late submission




































